Multi-Instance Methods for Partially Supervised Image Segmentation

### 2013-08-14 exact_learning/paper.tex
Moving around a lot of sections, renaming conclusion to summary, starting to merge mil and semisupervised, starting to rework structur of pystruct and exact learning.

\section{Introduction}
Many classical computer vision applications such as stereo, optical flow, semantic
segmentation and visual grouping can be naturally formulated as image labeling tasks.

Arguably the most popular way to approach such labeling problems is via graphical
models, such as Markov random fields (MRFs) and conditional random fields (CRFs).
MRFs and CRFs provide a principled way of integrating local evidence and
modeling spacial dependencies, which are strong in most image-based tasks.

While in earlier approaches, model parameters were set by hand or using
cross-validation, more recently parameters are often learned using a max-margin
approach.

Most models employ linear energy functions of unary and pairwise interactions,
trained using structural support vector machines (SSVMs). While linear energy
functions lead to learning problems that are convex in the parameters, complex
constraints complicate their optimization. Additionally, inference (or more precisely
loss-augmented prediction) is a crucial part in learning, and can often not be
performed exactly, due to loops in the neighborhood graphs.  % TODO clean up!
Approximations in the inference then lead to approximate learning.

We look at semantic image segmentation, learning a model of pairwise
interactions on the popular MSRC-21 dataset.
The contribution of this work is threefold:
\begin{itemize}
    \item We analyze the simultaneous use of multiple approximate inference
        methods for learning SSVMs using the cutting plane method, relating
        approximate learning to the exact optimum.
    \item We introduce an efficient caching scheme to accelerate cutting plane
        training.
    \item We demonstrate that using a combination of under-generating and exact
        inference methods, we can learn an SSVM exactly in a practical
        application, even in the presence of loopy graphs.
\end{itemize}

@@

\subsection{The Cutting Plane Method}\label{cutting_plane}

When learning for structured prediction in the max-margin framework of
\citet{tsochantaridis2006large}, predictions are made as
\[ \argmax_{y \in \mathcal{Y}} f(x, y, \theta),\]
where $x \in \mathcal{X}$ is the input, $y \in \mathcal{Y}$ the prediction, and $\theta$ are the parameters to be learned.
We will assume $y$ to be multivariate, $y=(y_1, \dots, y_k)$ with possibly varying $k$.

The function $f$ measures compatibility of $x$ and $y$ and is a linear function of the parameters $\theta$:
\[f(x, y, \theta) = \langle \theta, \psi(x, y) \rangle.\]
Here $\psi(x, y)$ is a joint feature vector of $x$ and $y$. Specifying a particular SSVM model
amounts to specifying $\psi$.

For a given loss $\Delta$, the parameters $\theta$ are learned by minimizing
the loss-based soft-margin objective
\begin{equation}\label{eq:mainequation}
\min_\theta \frac{1}{2} ||\theta||^2 + C \sum_i  r_i(\theta)
\end{equation}
with regularization parameter $C$, where $r_i$ is a hinge-loss-like upper
bound on the empirical $\Delta$-risk:
\[r_i(x^i, y^i, y) = \left [\max_{y \in \mathcal{Y}} \Delta(y^i, y) + \left<\theta, \psi(x^i, y) - \psi(x^i, y^i) \right > \right]_+ \]

We solve the following reformulation of Equation~\eqref{mainequation}, known as one-slack QP formulation:
\begin{align}\label{eq:oneslack}
    \min_{\theta, \xi}\ &\frac{1}{2} ||\theta||^2 + C \xi\\
    \text{s.t. }&\forall \hat{\mathbf{y}}=(\hat{y}^1, \dots, \hat{y}^n) \in \mathcal{Y}^n:\\
        &\left \langle \theta, \sum_{i=1}^n [\psi(x^i, y^i) - \psi(x^i,
            \hat{y}^i)] \right \rangle \geq \sum_{i=1}^n \Delta(y^i, \hat{y}^i)
            - \xi
\end{align}
using the cutting plane method described in
Algorithm~\ref{alg_cutting_plane}~\citep{joachims2009cutting}.

The cutting plane method alternates between solving Equation~\eqref{oneslack}
with a working set $\W$ of constraints, and expanding the working set using the
current $\theta$ by finding $\mathbf{y}$ corresponding to the most violated constraint,
using a separation oracle $I$.
We investigate the construction of $\W$ and the influence of $I$
on learning.

%TODO unstructured!!

Intuitively, the one-slack formulation corresponds to joining all training
samples into a single training example $(\mathbf{x}, \mathbf{y})$ that has no
interactions between variables corresponding to different data points.
Consequently, only a single constraint is added in each iteration of
Algorithm~\ref{alg_cutting_plane}, leading to very small $\W$. We further use
pruning of unused constraints, as suggested by \citet{joachims2009cutting},
resulting in the size of $\W$ being in the order of hundreds for all experiments.

We also use another enhancement of the cutting plane algorithm introduced by
\citet{joachims2009cutting}, the caching oracle. For each training example $(x^i, y^i)$,
we maintain a set $C^i$ of the last $r$ results of loss-augmented inference
(line~\ref{get_cutting_plane} in Algorithm~\ref{alg_cutting_plane}).
For generating a new constraint $(\hat{y}^1, \dotsc, \hat{y}^n)$ we find
\[ 
    \hat{y}^i \leftarrow \argmax_{\hat{y}\in C^i} \sum_{i=1}^n \Delta(y^i, \hat{y}) - \left \langle \theta, \sum_{i=1}^n [\psi(x^i, y^i) - \psi(x^i, \hat{y})] \right \rangle
\]
by enumeration of $C^i$ and continue until line~\ref{convergence_check}.
Only if $\xi' - \xi < \epsilon$, i.e.\ the produced constraint is not violated, we
return to line~\ref{get_cutting_plane} and actually invoke the separation
oracle $I$.

In computer vision applications, or more generally in graph labeling problems,
$\psi$ is often given as a factor graph over $y$, typically using only unary and pairwise functions:
\[ \langle \theta, \psi(x, y) \rangle = \sum_{i=0}^k \langle \theta_u,  \psi_u(x, y_k) \rangle + \sum_{(i, j) \in E} \langle \theta_p, \psi_p(x, y_k, y_l) \rangle, \]
where $E$ a set of pairwise relations. In this form, parameters $\theta_u$ and $\theta_p$ for unary and
pairwise terms are shared across all entries and pairs.
The decomposition of $\psi$ into only unary and pairwise interactions allows
for efficient inference schemes, based on message passing or graph cuts.

>>>>

\section{Introduction}
% Remove duplication with pystruct intro
As discussed previously, many computer vision algorithms empoy conditional random
field models on pixel or superpixel graphs. These graphs by nature contain loops,
making exact prediction and loss-augmented prediction intractable.
As loss-augmented prediction is a centreal step in the learning algorithms
discussed in Chapter~\ref{ch:structured_pystruct}
in the inference then lead to approximate learning.

In this chapter, we investigate the impact of these approximations in
the one-slack learning algorithms in the context of semantic 
image segmentation. We show that despite inference being deemed intractable in
loopy superpixel models, we are able to learn a structured support vector machine
for this application exactly.
learning a model of pairwise
We will evaluate our approach on the popular MSRC-21 and Pascal VOC datasets.

The contribution of this chapter is threefold:
\begin{itemize}
    \item We analyze the simultaneous use of multiple approximate inference
        methods for learning SSVMs using the cutting plane method, relating
        approximate learning to the exact optimum.
    \item We introduce an efficient caching scheme to accelerate cutting plane
        training.
    \item We demonstrate that using a combination of under-generating and exact
        inference methods, we can learn an SSVM exactly in a practical
        application, even in the presence of loopy graphs.
\end{itemize}

@@

### 2013-08-14 intro.tex
update jmlr paper in thesis
Moving around a lot of sections, renaming conclusion to summary, starting to merge mil and semisupervised, starting to rework structur of pystruct and exact learning.

Why semantic segmentation?
Why is it not solved yet?

@@

>>>>

Why semantic segmentation? Difference object / stuff centric? -> difference to Alex
Why is it not solved yet?

@@

Structured approaches, latent variable approaches

Contributions:
- Introduces general clustering algorithm that improves pipeline in serveral places
- Shows that weakly supervised object class segmentation (not semantic segmentation) is possible
- Provides general efficient framework for structured prediction
- Analyze max-margin learning algorithms in different regimes
- shows exact learning is possible in loopy graphs and improves results (sometimes?)
- shows importance of edge features
- Demonstrates how latent variables benefit semantic segmentation

### 2013-08-14 itm/paper.tex
Moving around a lot of sections, renaming conclusion to summary, starting to merge mil and semisupervised, starting to rework structur of pystruct and exact learning.

Before going to segmentation, we look at clustering because:
1 we see how far we can go without supervision
2 we need it as building block for bow
3 we need it as initialization for latent variable models
%TODO elaborate

Clustering data is one of the fundamental problems in machine learning.  In
clustering, the goal is to divide data points into homogeneous subsets, called
clusters.
Many different formulations of the clustering problem are given in the literature.
Most algorithms are based on ad-hoc criteria such as intra-cluster similarity
and inter-cluster dissimilarity.
%
An alternative approach is to formalize clustering using an information
theoretic framework, where one considers inputs as well as cluster assignments
as random variables.  The goal is then to find an assignment of data points to
clusters that maximizes the mutual information between the assignments and the
observations.

In this work, we rely on a non-parametric estimator of the data entropy to find 
clusterings of maximum mutual information.
%
The use of non-parametric estimates allows a data-driven approach, without 
making strong assumptions on the form of the data distribution.
%
As a consequence, we obtain a very flexible model that, e.g{.}, allows 
non-convex clusters.
%
The resulting objective is easy to evaluate, but difficult to optimize
over. We overcome this by proposing an efficient approximate optimization
based on the Euclidean minimum spanning tree algorithm. 
%
Because the estimator and the optimization are both parameter-free, 
the only free parameter of the algorithm is the number of clusters, 
which makes it very easy to use in practice.
%
The contributions of this work are:
\begin{itemize}
    \item Proposing the use of a MST-based entropy estimator in information theoretic clustering.
    \item Give a fast algorithm for a relaxed version of the resulting problem.
    \item Show the practicality on a number of synthetic and real datasets.
\end{itemize}

@@

\section{Related Work}
The most commonly used clustering algorithm is the $k$-Means algorithm, also
known as Lloyd's algorithm \citep{macqueen1967some,lloyd1982least}. While
$k$-Means often works well in practice, one of its main drawbacks is the
restriction in cluster shape. 
%
They are given by the Voronoi tessellation of the cluster means and therefore always convex.
%Not only are clusters as found by $k$-Means convex,
%they are given by the Voronoi tessellation of the cluster means.

@@

For the above reasons, we propose a simple procedure to approximately solve
\eqref{objective}.
%filler removed Let us first fix some notation.
Consider a graph $G$ with nodes $\mathbf{x}$ and edge weights given by the
Euclidean distances between points.  The connected components of $G$ induce a
clustering $\mathbf{y}(G)$ of $\mathbf{x}$, by assigning $x_i$ and $x_j$ the
same cluster if and only if they are in the same connected component of $G$.
Define
%\setlength{\abovedisplayskip}{1mm}
%\setlength{\belowdisplayskip}{1mm}
\begin{align}\label{eq:graphobjective}
\hat{I}(G) := - \sum_{y=0}^k p(y) \Bigl[ d \log(L_{G,y}) - (d-1) \log{n_y} \Bigr],
\end{align}
where $y$ enumerates the connected components $G_0, \dotsc, G_k$ of $G$, $n_y =
|V(G_y)|$ is the number of nodes in $G_y$ and $L_{G,y} = \sum_{e \in E(G_y)}
w(e)$ is the sum of the weights of all edges in the connected component $G_y$.
%
Then $\hat{I}(G) \geq \hat{I}(\mathbf{x}, \mathbf{y}(G))$, by the definition of
the minimum spanning tree, and equality holds if and only if $G_y$ is the
minimum spanning tree of its nodes for all $y$.
%
We try to find a graph $G$ with $k$ components, such that $\hat{I}(G)$ is maximal. We can restrict
ourself to optimizing over the set $\mathcal{F}$ of forests over $\mathbf{x}$ with $k$ components,
as adding edges inside connected components will only decrease the objective.
Thus we can formulate the clustering problem equivalently as
$\displaystyle \max_{G \in \mathcal{F}} \hat{I}(G)$.

@@

\section{Conclusions}
In this work we proposed the use of a minimum spanning tree based,
non-parametric entropy estimator in information theoretic clustering, ITM\@.
Thereby we extended the work of \citet{faivishevsky2010nonparametric} to a more
flexible and efficient entropy estimate.  We proposed an approximate optimization
method by formulating the clustering problem as a search over graphs.
The resulting algorithm is deterministic has sub-quadratic run time.
%
Empirical comparisons showed that the proposed method outperforms standard
algorithms and the non-parametric entropy based clustering of
\citep{faivishevsky2010nonparametric} on multiple benchmark datasets. We
demonstrated that ITM is able to detect non-convex clusters,
even in the presence of noise.
%
In contrast to other algorithms that can handle non-convex clusters, ITM has no
tuning parameters, as the objective presents a natural trade-off between
balancing cluster sizes and enforcing intra-cluster similarity.

A limitation of the proposed algorithm is that it is based on the assumption 
of an absolute continuous data distribution. This assumption eliminates the 
possibility of using categorical variables and data that lies on a submanifold 
of the input space. 
%
In future work we plan to investigate a way to overcome this limitation, 
for example by estimating the intrinsic dimensionality of the 
data~\citep{pettis1979intrinsic}.
%
We will also investigate optimizations of the objective 
\eqref{graphobjective} that go beyond the proposed method. 
Move-making algorithms seem a promising way to refine solutions 
found by Algorithm~1. Branch and bound techniques could provide 
an alternative approach.

>>>>

Before we start our investigation of semantic segmentation and object class segmentation,
we will look into a general purpose clustering algorithm.

In clustering, the goal is to divide data points into homogeneous subsets, called
clusters.
Many different formulations of the clustering problem are given in the literature.
%
In the context of this work, clustering plays an important role in many respects:
\begin{itemize}
    \item Clustering, as a purely unsupervised methods is on one end of the spectrum of algorithms we investigate.
        When using per-image or per-pixel supervision as in the later chapters, we can use clustering to calibrate our
        expecation of what semisupervised and supervised algorithms have at least to achieve.
    \item As many other computer vision algorithms, our segmentation methods
        with critically depend on bag-of-feature representations of segments or
        images. These are build using a vocabulary of visual words, that is
        usually created via clustering.
    \item When discussing latent variable models in chapter~\ref{ch:latent}, we need to initialize our
        model to overcome the inherant symmetries. Clustering methods are a
        straight forward solution to this problem.
\end{itemize}

So not only is clustering one of the fundamental problems in machine learning, it is also
an imortant building block for the methods in this work.
%
Most algorithms are based on ad-hoc criteria such as intra-cluster similarity
and inter-cluster dissimilarity.
An alternative approach is to formalize clustering using an information
theoretic framework, where one considers inputs as well as cluster assignments
as random variables.  The goal is then to find an assignment of data points to
clusters that maximizes the mutual information between the assignments and the
observations.

In the following, we rely on a non-parametric estimator of the data entropy to find 
clusterings of maximum mutual information.
%
The use of non-parametric estimates allows a data-driven approach, without 
making strong assumptions on the form of the data distribution.
%
As a consequence, we obtain a very flexible model that, e.g{.}, allows 
non-convex clusters.
%
The resulting objective is easy to evaluate, but difficult to optimize
over. We overcome this by proposing an efficient approximate optimization
based on the Euclidean minimum spanning tree algorithm. 
%
Because the estimator and the optimization are both parameter-free, 
the only free parameter of the algorithm is the number of clusters, 
which makes it very easy to use in practice.
%
The contributions of this chapter are:
\begin{itemize}
    \item Proposing the use of a MST-based entropy estimator in information theoretic clustering.
    \item Give a fast algorithm for a relaxed version of the resulting problem.
    \item Show the practicality on a number of synthetic and real datasets.
\end{itemize}

@@

\section{Related Work}
The most commonly used clustering algorithm is the $k$-Means algorithm, also
known as Lloyd's algorithm \citep{macqueen1967some,lloyd1982least}. While
$k$-Means often works well in practice, one of its main drawbacks is the
restriction in cluster shape. 
%
They are given by the Voronoi tessellation of the cluster means and therefore always convex.
Another draw-back is the non-determinism of the procedure, caused by the
dependence on random initialization.

@@

For the above reasons, we propose a simple procedure to approximately solve
\eqref{objective}.
%filler removed Let us first fix some notation.
Consider a graph $G$ with nodes $\mathbf{x}$ and edge weights given by the
Euclidean distances between points.  The connected components of $G$ induce a
clustering $\mathbf{y}(G)$ of $\mathbf{x}$, by assigning $x_i$ and $x_j$ the
same cluster if and only if they are in the same connected component of $G$.
Define
\begin{align}\label{eq:graphobjective}
\hat{I}(G) := - \sum_{y=0}^k p(y) \Bigl[ d \log(L_{G,y}) - (d-1) \log{n_y} \Bigr],
\end{align}
where $y$ enumerates the connected components $G_0, \dotsc, G_k$ of $G$, $n_y =
|V(G_y)|$ is the number of nodes in $G_y$ and $L_{G,y} = \sum_{e \in E(G_y)}
w(e)$ is the sum of the weights of all edges in the connected component $G_y$.
%
Then $\hat{I}(G) \geq \hat{I}(\mathbf{x}, \mathbf{y}(G))$, by the definition of
the minimum spanning tree, and equality holds if and only if $G_y$ is the
minimum spanning tree of its nodes for all $y$.
%
We try to find a graph $G$ with $k$ components, such that $\hat{I}(G)$ is maximal. We can restrict
ourself to optimizing over the set $\mathcal{F}$ of forests over $\mathbf{x}$ with $k$ components,
as adding edges inside connected components will only decrease the objective.
Thus we can formulate the clustering problem equivalently as
\begin{equation}
    \max_{G \in \mathcal{F}} \hat{I}(G).
\end{equation}

@@

\section{Summary}
In this summary we proposed the use of a minimum spanning tree based,
non-parametric entropy estimator in information theoretic clustering, ITM\@.
Thereby we extended the work of \citet{faivishevsky2010nonparametric} to a more
flexible and efficient entropy estimate.  We proposed an approximate optimization
method by formulating the clustering problem as a search over graphs.
The resulting algorithm is deterministic has sub-quadratic run time.
%
Empirical comparisons showed that the proposed method outperforms standard
algorithms and the non-parametric entropy based clustering of
\citep{faivishevsky2010nonparametric} on multiple benchmark datasets. We
demonstrated that ITM is able to detect non-convex clusters,
even in the presence of noise.
%
In contrast to other algorithms that can handle non-convex clusters, ITM has no
tuning parameters, as the objective presents a natural trade-off between
balancing cluster sizes and enforcing intra-cluster similarity.

%A limitation of the proposed algorithm is that it is based on the assumption 
%of an absolute continuous data distribution. This assumption eliminates the 
%possibility of using categorical variables and data that lies on a submanifold 
%of the input space. 
%
%In future work we plan to investigate a way to overcome this limitation, 
%for example by estimating the intrinsic dimensionality of the 
%data~\citep{pettis1979intrinsic}.
%
%We will also investigate optimizations of the objective 
%\eqref{graphobjective} that go beyond the proposed method. 
%Move-making algorithms seem a promising way to refine solutions 
%found by Algorithm~1. Branch and bound techniques could provide 
%an alternative approach.

### 2013-08-14 mil/paper.tex
Moving around a lot of sections, renaming conclusion to summary, starting to merge mil and semisupervised, starting to rework structur of pystruct and exact learning.

\section{Introduction}\seclabel{intro}
Multiple instance learning is a supervised learning scenario first proposed by \citet{dietterich1997solving}.
In multiple instance learning, examples are multi sets of instances, called bags, and each bag is assigned a class label.
It is assumed that each instance has a true label, defined by an underlying concept. The label of a bag is positive, if and only if one of
the instances it contains is labeled positive. The true label of instances is assumed to be unobserved by the learner who only has access to bag labels.

@@

Learning to predict instance labels has been attempted in some recent work~\citep{liconvex2010,zhang2002dd}
but there has been very little theoretical study when and to which extend this is possible.
In this work, we explore which assumptions about the distributions of instances and labels
are necessary to learn instance-level classifiers from bag labels only.
We provide bounds on the instance label prediction error based on the
bag label prediction error. The bounds can be used to judge a learner when no
instance labeling exists for training or testing.
%If one is interested in classifying instances, such a bound is very important.
There are two applications that we target:
\begin{description}
\item[Setting 1:] Bag labels for a validation set are known and instance predictions need to be judged.
\item[Setting 2:] Bag labels for a test set can be bound using standard learning theoretic bounds and instance
predictions need to be judged.
\end{description}
The first case is very common in practical settings, where
cross validation is often used to set parameters of a predictor. This is
particularly important in support vector machines (SVMs) which are a popular
learning method for multiple instance problems~\citep{andrews2003support}.
If no instance labels are present for training, it is only possible to
choose parameters to minimize bag prediction error, which might be suboptimal if one
wants to minimize instance label misclassification. 
The bounds can also be used to find the amount of positive instances in positive bags,
known as the witness rate, which is an integral part of established multiple
instance algorithms~\citep{zhang2002dd,liconvex2010}.
The second case can be used to convert established bounds on the bag prediction error
to instance prediction error.

@@

\section{Conclusion}
We provided several bounds on instance prediction error in a multiple instance learning setting.
For the case that instances inside a bag are independent, we proved a strong upper bound on the error.
We showed that when bag labels are present, it is even possible to directly estimate the true instance error.

@@

\section{Appendix}
\begin{lemma}\label{binarylemma}
Given two (dependent) binary random variables $x,y$:
\begin{equation}
p(x \neq y) = p(x=0) + p(y=0) - 2 p(x=0, y=0)
\end{equation}

\begin{proof}
\begin{align}
p(x \neq y) & = p(x=0, y=1) + p(x=1, y=0) \\
                &= p(x=0) - p(x=0, y=0)\\
                &  + p(y=0) - p(x=0, y=0) \\
                &= p(x=0) + p(y=0) -2 p(x=0, y=0)
\end{align}
\end{proof}
\end{lemma}

\begin{theorema}
Let all instances be independent. With bags $X$, instances $x$, true labels $y,Y$, $h_I$ any classifier
on instances and $h_B$ the resulting bag classifier, we have
\begin{align*}
   e_I = h_0 + p(y=0) - 2 \left (\frac{1}{2} ( h_0^r + p(y=0)^r - e_B) \right)^\frac{1}{r}
\end{align*}
\begin{proof}

\begin{align*}
e_B & = p(h_B(X) = 0) + p(Y=0) -2 p(h_B(X)=0, Y=0) \\\
&\text{using the lemma}\\
& = h_0^r + p(y=0)^r -2 p(h_I(x)=0, y=0)^r\\\
&\text{by independence}\\
& = h_0^r + p(y=0)^r -2 \left ( \frac{1}{2} (h_0 + p(y=0) - e_I) \right ) ^r \\
&\text{using Lemma~\ref{binarylemma} on }p(h_I(x)=0, y=0.
\end{align*}
Solving for $p(h_I(x)\neq y)$:
\begin{align*}
    & \left ( \frac{1}{2} (h_0 + p(y=0) - e_I )\right ) ^r = \frac{1}{2} \left ( h_0^r + p(y=0)^r - e_B \right )\\
    & \Rightarrow \frac{1}{2} (h_0 + p(y=0) - e_I)   = \left ( \frac{1}{2} \left ( h_0^r + p(y=0)^r - e_B \right ) \right )^\frac{1}{r}\\
    & \Rightarrow e_I   = h_0 + p(y=0) - 2 \left ( \frac{1}{2} \left ( h_0^r + p(y=0)^r - e_B \right ) \right )^\frac{1}{r}
\end{align*}
\end{proof}
\end{theorema}

\begin{corollarya}
If all instances are independent and bag classification is perfect, meaning $e_B=0$, then instance classification is also perfect ($e_I =0$).

\begin{proof}
Consider Theorem~\ref{basicthm}. If $e_B=0$ we have
\begin{align*}
p(h_I(x) \neq y) = h_0 + p(y=0) - 2 \left (\frac{1}{2} ( h_0^r + p(y=0)^r)) \right)^\frac{1}{r}
\end{align*}
By the convexity of the power function the right hand side of the equation is always greater or equal zero.
Since $e_I \geq 0$, both sides are equal zero.
\end{proof}
\end{corollarya}

\begin{theorema}
    If $h_0^r  \geq e_B$ and all instances are independent, we have
\begin{align}
    p(h_I(x)\neq y) \leq h_0 - \left ( h_0^r - e_B) \right ) ^ \frac{1}{r}
\end{align}
\begin{proof}
    Assume $h_0^r  \geq e_B$.
    From Theorem~\ref{basicthm} we have
\begin{align*}
   e_I &= h_0 + p(y=0) - 2 \left (\frac{1}{2} ( h_0^r + p(y=0)^r - e_B) \right)^\frac{1}{r}\\
   &\leq h_0 + p(y=0) - \left [( h_0^r + p(y=0)^r - e_B) \right]^\frac{1}{r}\\
   &- \left ( p(y=0)^r \right )^\frac{1}{r}\\
   &= h_0 - \left (( h_0^r + p(y=0)^r - e_B) \right)^\frac{1}{r}\\
\end{align*}
\end{proof}
\end{theorema}

\begin{theorema}
Let all instances be independent. Given $p(Y)$, the instance error $e_I$ can be calculated by
\begin{align}
    %\eqlabel{iid}
e_I = h_0 + p(Y=0)^\frac{1}{r} - 2 \left (\frac{1}{2} ( h_0^r + p(Y=0) - e_B) \right)^\frac{1}{r}.
\end{align}
\begin{proof}
    This follows from Theorem~\ref{basicthm} by using $p(Y=0)=p(y=0)^r$.
\end{proof}
\end{theorema}

\begin{theorema}
If the instance labels are independent inside a bag given a hidden cause, the instance
error $e_I$ has the following lower bound:
\begin{multline*}
e_I \geq h_0 + p(y=0) - \\
2 \left (\frac{1}{2} (p(h_B(X)=0) + p(Y=0) - e_B) \right)^\frac{1}{r}
\end{multline*}
\begin{proof}
    This follows from taking the expected value with respect to $Z$ of \eqref{conditioned} and using Jensen's
    inequality.
\end{proof}
\end{theorema}

>>>>

\section{Theoretical settings}\seclabel{intro}
Multiple instance learning is a supervised learning scenario first proposed by \citet{dietterich1997solving}.
In multiple instance learning, examples are multi sets of instances, called bags, and each bag is assigned a class label.
It is assumed that each instance has a true label, defined by an underlying concept. The label of a bag is positive, if and only if one of
the instances it contains is labeled positive. The true label of instances is assumed to be unobserved by the learner who only has access to bag labels.

@@

Learning to predict instance labels has been attempted in some recent work~\citep{liconvex2010,zhang2002dd}
but there has been very little theoretical study when and to which extend this is possible.
In this work, we explore which assumptions about the distributions of instances and labels
are necessary to learn instance-level classifiers from bag labels only.
We provide bounds on the instance label prediction error based on the
bag label prediction error. The bounds can be used to judge a learner when no
instance labeling exists for training or testing.

%If one is interested in classifying instances, such a bound is very important.
There are two applications that we target:
\begin{description}
\item[Setting 1:] Bag labels for a validation set are known and instance predictions need to be judged.
\item[Setting 2:] Bag labels for a test set can be bound using standard learning theoretic bounds and instance
predictions need to be judged.
\end{description}
The first case is very common in practical settings, where
cross validation is often used to set parameters of a predictor. This is
particularly important in support vector machines (SVMs) which are a popular
learning method for multiple instance problems~\citep{andrews2003support}.
If no instance labels are present for training, it is only possible to
choose parameters to minimize bag prediction error, which might be suboptimal if one
wants to minimize instance label misclassification. 
The bounds can also be used to find the amount of positive instances in positive bags,
known as the witness rate, which is an integral part of established multiple
instance algorithms~\citep{zhang2002dd,liconvex2010}.
The second case can be used to convert established bounds on the bag prediction error
to instance prediction error.

@@

\section{Summary}
We proposed an algorithm for object-class segmentation using only weak supervision based on
multiple-instance learning. In our approach each image is represented as a bag of object-like
proposal segments.

We described a way to extent bag level predictions made by the multi-instance
kernel method to instance level while remaining competitive with the state-of-the-art
in bag label prediction.

We evaluated the proposed object-class segmentation method on the challenging
Graz02 dataset. While not reaching the performance of methods using strong supervision,
our result can work as a baseline for further research into weakly supervised object class
segmentation.

%In future work, we plan to scale our approach to much larger image datasets. As much
%more images with weak annotations are available than with pixel level segmentation,
%we hope that we can improve upon the state-of-the-art in object-class segmentation
%by making use of larger bodies of training images.
On the theoretical side, we provided several bounds on instance prediction
error in a multiple instance learning setting.  For the case that instances
inside a bag are independent, we proved a strong upper bound on the error.  We
showed that when bag labels are present, it is even possible to directly
estimate the true instance error.

@@

### 2013-08-14 partial_supervision/paper.tex
Moving around a lot of sections, renaming conclusion to summary, starting to merge mil and semisupervised, starting to rework structur of pystruct and exact learning.

The task of multi-class image segmentation is to create a pixel-wise labeling of an input image
into regions belonging to one of several semantic classes.
Most algorithms for this setting work with strong supervision: a pixel-wise labeling
of training images. Methods that are used in this setting include random forests~\citep{schroff2008object} and support vector machines (SVM). Usually
the output of such algorithms is further processed by a conditional random field (CRF~\citep{ladicky2009associative,gonfaus2010harmony,jiang2009efficient}).
While these methods reach high accuracy, it is very time consuming to create
pixel-level ground truth for real-world applications.
This problem can be addressed in several ways:
the LabelMe effort~\citep{russell2008labelme} tries to use the ``wisdom of crowds'' to obtain human labelings.
Another possibility is to use only weak supervision, which is the approach we follow here.

In the weakly supervised setting, the ground
 truth for a given image is a list of semantic classes that occur in this image, instead of a pixel-level
labeling as in the strongly supervised setting.
Image-level labels are much easier to obtain, e.~g.\  through online image libraries such as flickr and facebook.

@@

In this work, we explore the 
application of multi-instance learning algorithms to the task of partially supervised image segmentation.
Multi-instance learning is a natural formulation for image classification and has been
successfully applied in this task~\citep{zhou2007multi}. We propose to go a step further and apply
multi-instance learning to the task of object-class segmentation in natural
images. To our knowledge, all previous
methods in the field use strong supervision, meaning manual pixel-wise annotation of
training images. This approach does not
scale to larger datasets, especially if one expects consistency and quality
in the segmentations.

@@

\subsection{Multi-Instance Methods}
Multi-instance learning was formally introduced in \citet{dietterich1997solving}.
Since then, many algorithms were proposed to solve the multi-instance learning problem
using many different approaches \citep{andrews2003support,gaertner2002multi,zhou2009multi,li2009convex,zhang2002dd,mangasarian2008multiple,leistner2010miforests,chen2006miles}.
We will discuss only those that are relevant to this work.

@@

\section{Multi-Instance Kernels for Image Segmentation}
\subsection{Constraint Parametric Min Cuts (CPMC)}
To generate proposal segments, we use the CPCM framework from \citet{carreira2010constrained}. We construct initial
segments using graph cuts, on the image graph. The energy function for these cuts uses pixel
color and the response of the global probability of boundary (gPb) detector~\citep{maire2008using}. As much as ten thousand initial segments are generated from foreground
and background seeds. A fast rejection based on segment size and ratio cut~\citep{wang2003image} reduced these to about 2000 overlapping
segments per image. Then, the segments are ranked according to a measure of object-likeness that is based on region and Gestalt properties.
This ranking is computed using an SVR model~\citep{carreira2010constrained}, which is available online.
For computing the global probability of boundary (gPb), we used the CUDA implementation
of \citet{catanzaro2009efficient}, instead of the original one, for speed.

@@

\section{Conclusions}
We proposed an algorithm for object-class segmentation using only weak supervision based on
multiple-instance learning. In our approach each image is represented as a bag of object-like
proposal segments.

We described a way to extent bag level predictions made by the multi-instance
kernel method to instance level while remaining competitive with the state-of-the-art
in bag label prediction.

Finally we evaluated the proposed object-class segmentation method on the challenging
Graz02 dataset. While not reaching the performance of methods using strong supervision,
our result can work as a baseline for further research into weakly supervised object class
segmentation.

In future work, we plan to scale our approach to much larger image datasets. As much
more images with weak annotations are available than with pixel level segmentation,
we hope that we can improve upon the state-of-the-art in object-class segmentation
by making use of larger bodies of training images.

>>>>

Most algorithms for semantic image segmentation and object-class segmentation work with strong supervision: a pixel-wise labeling
of training images. In this chapter, we will investigate a method that works with annotation
that is much easier to obtain: whole image labels.

% TODO contrast with Alex

@@

This chapter explores the 
application of multi-instance learning algorithms to the task of partially supervised image segmentation.
Multi-instance learning is a natural formulation for image classification and has been
successfully applied in this task~\citep{zhou2007multi}. We propose to go a step further and apply
multi-instance learning to the task of object-class segmentation in natural
images.
% FIXME relate to alex here
To our knowledge, all previous methods in the field use strong
supervision, meaning manual pixel-wise annotation of training images. This
approach does not scale to larger datasets, especially if one expects
consistency and quality in the segmentations.

After our empirical evaluation on image segmentation, we will extend the existing theoretical framework
on instance classification based on multi-instance prediction.

@@

\subsection{Multi-Instance Methods}
Multi-instance learning was formally introduced in \citet{dietterich1997solving}.
Since then, many algorithms were proposed to solve the multi-instance learning problem
using many different approaches \citep{andrews2003support,gaertner2002multi,zhou2009multi,li2009convex,zhang2002dd,mangasarian2008multiple,leistner2010miforests,chen2006miles}.
We will discuss only those that are relevant to the present treatment.

@@

\section{Multi-Instance Kernels for Image Segmentation}
\subsection{Constraint Parametric Min Cuts (CPMC)}
To generate proposal segments, we use the Constraint Parametric Min Cut (CPCM) method from \citet{carreira2010constrained}. In CPMC, initial
segments are constructed graph cuts on the pixel grid. The energy function for these cuts uses pixel
color and the response of the global probability of boundary (gPb) detector~\citep{maire2008using}. As much as ten thousand initial segments are generated from foreground
and background seeds. A fast rejection based on segment size and ratio cut~\citep{wang2003image} reduced these to about 2000 overlapping
segments per image. Then, the segments are ranked according to a measure of object-likeness that is based on region and Gestalt properties.
This ranking is computed using an SVR model~\citep{carreira2010constrained}, which is available online.
For computing the global probability of boundary (gPb), we used the CUDA implementation
of \citet{catanzaro2009efficient}, instead of the original one, for speed.

@@
